---
title: "A Short Introduction to the kinn Package"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Description

This is a tutorial which explains the main idea behind kinn algorithm  and demonstrates a usage of the kinn package for regression.  

### Algorithm
The process begins by building a graph G(V,E) from a given training set.  
At first, V nodes groups in G(V,E) is defined as the training set (X,Y).  
Then the number of neighbours/edges in the graph, hence |E| is calculated proportionally to the noise of the data taking E(Y|X) as a measure of it. 
(The nosier the data - the more edges are allocated in order to smooth the noise)  
Once the number of edges |E| is calculated, the edges group E itself is created  by allocating edges according to node to node similarity.
The  similar nodes are, the more chance that an edge between them
will be formed and added to the edges set E graph during edge allocation process.  
Given G(V,E), we can now predict x by:

* Finding the most similar node to x the graph  
* Evaluating a predictor $\hat{y}$ by averaging most similar y(x) independent variable and it's neighbours (all y's of the neighbours)

_Note that as oppose to 'knn' which has k fixed nearest neighbours,each node in 'kinn' graph may have a **variable** number of neighbours allocated to it._  

### Usage

The predicition process begins by training the dataset using _kinn.train_
which returns a kinn model

```{r }
library(kinn)
#create training dataset
x<-runif(100,min=1,max=10)
y<-2*x+3+rnorm(100)
df = data.frame(x,y)
#train the model
model= kinn.train("y~x",df)
```

Once the model is created, we can now make predictions by _kinn.predict_ 

```{r kinn}
#create test dataset
x<-runif(50,min=1,max=10)
y<-2*x+3+rnorm(50)
df = data.frame(x,y)

#make predictions
yhat= kinn.predict(model,df)
plot(x,y,type="p",pch=19,col="red")
points(x,yhat,col="green")

# plot predictors and test groups 
legend("topright",  c("y","kinn y"),  
lty=c(1,1), lwd=c(2.5,2.5),col=c("red","green")) 
```

And plot the model subgraphs using _kinn.plot_

```{r kinn model}
kinn.plot(model)
```
